Two-Dimensional Vesicle Hydrodynamics from Hydrophobic Attraction Potential

### 2022-02-15 doc/reviews/ResponseToReviewer1.tex

\noindent
\comment{Equation (2.4) is not necessary as the no-slip boundary
condition is standard and it is redundant with (2.5).}
\begin{itemize}
  \item We deleted the redundant equation (2.5) mentioned by the Reviewer.
\end{itemize}

\noindent
\comment{Section 2.2: for clarity, define the variable u as the
hydrophobic attraction potential in the first paragraph.}

\noindent
\comment{The equations of the continuous time evolution of the particle
positions and orientations should be written in Section 2 to close the
problem.}
\begin{itemize}
  \item Section 2.2 introduces the imposed forces and torques in hydrophobic attraction and repulstion that are not used to obtain particle directions directly. Following the next comment by 
the Reviewer, we agreed that Section 2.3 should be moved to the end of Section 3 and we complete the change.
\end{itemize}

\noindent
\comment{I think the time-discretization Section 2.3 should go at the
end of Section 3 since this is the one devoted to the numerical
discretization of the governing equations. Also, the sentence ``particle
collisions are avoided even when using a relatively large time step" is
very vague.  What do you mean by ``relatively large time step"? Compared
to what time scale?}
\begin{itemize}
  \item We thank the Review for the comment and we moved the original Section 2.3 {\it Time Marching} at the end of Section 3 combining the change based on the comment previously addressed about what to solve for in the proposed algorithm. 
As described in Section 2.2, the repulsion force with a constant strength coefficient $M$ is chosen 
to be a large number in order to avoid particle collisions. If $M$ is not large enough, the hydrophobic attraction will dominate the total force and the dynamics may cause particle collisions with the use of a larger time step. Therefore, with an empirical study to the relationship between 
choices of M and $\gamma$, the parameter set in this work allows the time step to be as large as
$O(10^{-1})$ with no instability. Comparing the time step used in literatures, for instance, in Bystricky {\sl et al.}, {\bf 2020}, Int. J. Numer. Methods Fluids), $\Delta t\sim O(10^{-2})$.
\end{itemize}

\noindent
\comment{Section 3: the acronym HAP is not defined in the text.}
\begin{itemize}
  \item Thank you for noticing this oversight. The definition of HAP has
    been added at its first occurrence in Section 3.1. 
  \item This change is in \textcolor{green}{green} since it was also pointed
    out by Reviewer 2.
\end{itemize}

@@

\noindent
\comment{For clarity, use contraction products ``$\cdot$" when a second
order tensor multiplies a vector to avoid confusion (e.g.~${\bf S} \cdot
{\bf F}$ instead of ${\bf SF}$) in eqs.~(3.4), (3.5), (3.7) and so on
$\ldots$}
\begin{itemize}
  \item This notation has been adjusted throughout Section 3.
\end{itemize}

\noindent
\comment{In practice, how do you compute the derivatives $d\sigma /ds$,
$dv_i/ds$ and $dv_i/d\boldsymbol{\nu}$ in (3.13)?}
\begin{itemize}
  \item Since the only derivatives that are required are functions
    defined only on the boundary of the Janus particles, they are
    computed with spectrally-accurate Fourier differentiation.

  \item We have added the following sentence to the start of Section 3
    \begin{quotation}
      All derivatives are computed with spectrally-accurate Fourier
      differentiation.
    \end{quotation}
\end{itemize}

\noindent
\comment{Line 256: you set the strength of the repulsive force $M = 4k_B
T$. In your simulations there is no thermal fluctuations, so why using
$k_B T$ as a reference energy if it is no there in the simulations?
There should be another energy scale that you could use to calibrate
$M$, right?}
\begin{itemize}
  \item All physical quantities in membrane mechanics such as interfacial tension, bending  modulus, and energy constant in pairwise interactions are defined in units of $k_BT$. 
\end{itemize}

\noindent
\comment{Related question: how much does the interparticle distance
depend on on the strength and range of this artificial repulsive
potential? What is the impact on the vesicle shape and effective
properties?}
\begin{itemize}
  \item We tested the model parameters based on matching simulation results in the previous paper  (Fu {\sl et al.}, {\bf 2020}, Multiscale Model. Simul.). The proposed work adopts a different repulsion force from the previous one and we have done studies in choosing the default parameter set to achieve similar structures. For the effective properties, we leave it as a future work.
\end{itemize}

### 2022-02-15 doc/reviews/ResponseToReviewer2.tex

\noindent
\comment{What is the bending modulus here? I guess that it is not a
direct input parameter in this model but rather a quantity that can be
deduced from other input parameters. If I am right then, what are these
parameters? And could you tune them if needed to simulate the effect of
the membrane stiffness? This can be important in some applications such
as rigidity-based microfluidic sorting devices.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{To compare the results with the existing literature, I would
suggest introducing the capillary number for vesicles as defined in
\url{https://doi.org/10.1016/j.crhy.2009.10.001}.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{For both examples with the linear shear flow and the Poiseuille
flow, the area of the vesicle is not conserved and the relative error
with respect to the stress-free area increases with the increase of the
external stresses. It can reach roughly 7-8\% for the higher shear rate
in the shear flow example. This is quite significant. Do you have a way
to reduce this error to below 1\%? Note that in other numerical models
for vesicles (e.g.~\url{https://doi.org/10.1016/j.jcp.2008.11.036}),
both constant area and perimeter constraints are fulfilled even when the
vesicle is more deformed than the cases reported here.}
\begin{itemize}
  \item Change 1 
\end{itemize}

\noindent
\comment{In some interesting applications, the fluid encapsulated by the
bilayer membrane has a viscosity which is different from the suspending
fluid. How difficult it is to add this feature to your model?}
\begin{itemize}
  \item 
Our method currently does not support a viscosity contrast in the system 
or the setup similar to ones in (Veerapaneni {\sl et al.}, {\bf 2011}, Phys. Rev. Lett.),
(Vlahovska and Gracia, {\bf 2007}, Phys. Rev. E), and
(Kaoui and Harting, {\bf 2016}, Rheol Acta). 
As described in the manuscript, the JP vesicle is permeable and the mixture of two different
fluids has to be analyzed within the framework.

\end{itemize}

### 2022-02-15 doc/reviews/ResponseToReviewer3.tex

\noindent
\comment{{\bf 1.} In section 2.2, the authors defined a repulsion force with an
empirical formula to prevent particle collisions. However, there is no
benchmark test to show that this artificial repulsion force can generate
correct hydrodynamic lubrication. The authors are suggested to justify
and validate the use of the Imposed Forces with comparison to well-known
lubrication forces between particles.}
\begin{itemize}
  \item Response: The repulsive potential we used to prevent overlap of Janus particles is the repulsive Morse potential based on the electrostatic repulsive potential between two negatively (or positively) charged particles immersed in a medium of low electrolyte concentration so that there is a well-defined zeta potential on the charged particle (Coakley {\sl et al.}, 1999, Biophys. J). This repulsive potential has been approximated by the short-range repulsive Lennard-Jones potential (Flormann {\sl et al.}, 2017, Sci. Reports), which has been adopted by Quaife and Young to study the interaction between two membranes in a viscous solvent in Quaife, Veerapaneni and Young, 2019, Phys. Rev. Fluids, where Quaife {\sl et al.} showed that the lubrication hydrodynamics (draining of fluid between two membrane) is well captured and the scaling of lubrication thin film is recovered.

This is evidence that the lubrication hydrodynamics of the thin film between two particles under the repulsive Morse potential is well captured  if the flow velocity can be accurately calculated in the boundary integral simulations when two particles are sufficiently close to each other and the short-range repulsion is the dominant force.

In this work we use similar techniques for solving the integral equations when some boundaries are quite close to each other.  As the repulsive Morse potential works well to prevent overlapping of particles (provided the time step size is sufficiently small), our previous results in Quaife, Veerapaneni and Young, 2019, Phys. Rev. Fluids gives us confidence in the accuracy of the fluid flow in the thin space between the particles.

@@

\item Change: We added a short paragraph to describe our methodology to capture the lubrication flow in the space between particles in close vicinity of each other in page, between lines \$\$\$ and \$\$\$.

\end{itemize}

\noindent
\comment{{\bf 2.} Fig.~3 plots the time evolution of the reduced area in (a) and
the excess length of the bilayer structure in (b). Both show obvious
oscillations with multiple frequencies, which are not as smooth as the
inset of (c) showing one dominant frequency. The authors are suggested
to explain the source of multiple frequencies generated in the time
evolution of $A$ and $\Delta$.}
\begin{itemize}
  \item Fig.~3(c) clearly shows that the total length of the JP vesicle has a steady periodic motion 
which is different from the trends shown in panels (a) and (b). We showed the actual time evolution of $A^*$ and $\Delta$ and fitting curves in (a). 
The idea is to show that we can use the fitting data to acquire the numerical expected teminal 
reduced area $A^*_\infty$. Therefore the multiple frequencies during simulations have no correlations between
the output in (c) and (d).
\end{itemize}

\noindent
\comment{{\bf 3.} Fig.~6 illustrates the migration process of a JP vesicle in a
parabolic flow, where the moving velocity is 8 nm/ns and the time frame
is 0 to 12 $\mu$s. Given the length scale R = 20 nm, the migration
distance should be $1000 \times R$. However, in the figure, it shows a
migration distance about $4 \times R$. The authors are suggested to
double-check their model parameterization.}
\begin{itemize}
  \item Fig.~6 shows snapshots for 4 time frames from 0 to 12 $\mu$s and the trajectory of the centriod is demonstrated. Therefore the dashed horizontal line of Fig.~6 represents time in units of $\mu$s and the vertical axis represents the scaled $y$ position of the centroid of the JP vesicle.
\end{itemize}

\noindent
\comment{{\bf 4.} In Fig.~10, the significant discontinuities in streamlines
across the surface of vesicles are observed, while in most other cases
the streamlines are smooth across the interface of vesicles. The authors
are suggested to describe such discontinuity and provide the
explanation.}
\begin{itemize}
  \item We corrected the original Fig.~10 by plotting all continuous streamlines. We thank the Reviewer for pointing this out and this issue occurred due to a mistake made in post-processing
steps. Moreover, we do expect some discontinuous streamlines where it occurs when a strealine flows across the JP vesicle interface.
\end{itemize}

### 2022-02-15 doc/main_jfm.tex
updates
updated by Peter

% what we solve for?
\ReviewerOne{
\subsection{Time Marching}
To summarize, the proposed algorithm aims to obtain the JP velocities ${\bf v}_i$ and $\omega_i$. 
After calculating the imposed forces $\FF_i$ and torques $T_i$, 
two density functions $\sigma$ and  $\eeta$ are solved in the second-kind integral equations involving the HAP~\eqref{eq:screenedSKIE} and the mobility problem~\eqref{eq:SKIE}-\eqref{eq:mobility2} via GMRES.
%By solving the mobility problem, we obtain translational and angular
%velocities of the $N_b$-body system. 
Moreover, a second-order Adams-Bashforth
scheme updates the particle positions and orientations. By including the
repulsion force~\eqref{eq:REPULforce}, particle collisions are avoided even
when using a relatively larger time step than $\Delta t\sim O(10^{-1})$ ns. 
}

@@

%updated table
\begin{table}
\caption{Friction Coefficients $b$ (pN ns nm$^{-3}$) \\
}
\centering
\begin{tabular}{c c c c c c c c c }
& & & & $\dot\gamma$  (ns$^{-1}$) & & & &\\
\cline{2-8}\\
 & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  & Average\\
\cline{1-8}\\
$N_b=53$  & 0.50  & 0.51  &  0.44 & 0.52  & 0.45 &  0.57   &  0.62 & 0.52  \\ 
$N_b=56$ & 0.54 & 0.41 & 0.35  & 0.37 & 0.43 & 0.76  & 0.70 & 0.51\\ 
$N_b=58$   & 0.42 & 0.63 & 0.50   & 0.40  & 0.48  & 0.53 & 0.55 & 0.50 \\   % new
$N_b=61$  & 0.22 & 0.36 & 0.41   & 0.45  & 0.45 & 0.44   & 0.44 & 0.40\\ 
\end{tabular} 
\label{table1}
\end{table}

@@

%Table~\ref{table1} provides $b = 0.79 \pm 0.3$ pN ns nm$^{-3}$  
\ReviewerOne{Table~\ref{table1} provides a series of numerical friction coefficients $b$ and the default number of particles is $N_b = 58$. With the fixed total length of the JP vesicle, we change parameters related to the length scale, for instances, $\rho$, $\rho_0$, and the radius of particles.
With $-5\%$, $5\%$, and $10\%$ adjustments in these parameters, the resulting numbers of particles are $N_b=\{61,56,53\}$, respectively. }
%
\ReviewerOne{There is no clear trend shown in Table~\ref{table1} but these values of $b$ are}
%over a range of shear rates which is 
in good quantitative agreement with values previously reported in the literature.
Atomistic studies have also considered inter-monolayer slip in lipid bilayers. 
\cite{WuoEd06} and \cite{denOtter2007} reported $b = 0.7 \times 10^6$ Pa m$^{-1}$ s  
$=0.7$ pN ns nm$^{-3}$  
and $b = 2.4$  pN ns nm$^{-3}$ for DPPC membranes simulated by MD, respectively. 
Using a more recent version of the Martini force field, \cite{Zgorski2019} 
gives $b = 5.5$ pN ns nm$^{-3}$ for shear rates 0.4 ns$^{-1}$ and higher.
It is understandable that there is uncertainty in the friction coefficients of
Table~\ref{table1}.  The scatter in our data, however, is fully consistent with that calculated
from MD simulations, c.f. the transient rise in values of Table~\ref{table1} and in \cite{Zgorski2019}, Figure 10
for low shear rates. 
\subsubsection{Membrane Ruptures}
\begin{figure}
\centering
\includegraphics[width=11.32cm]{Figure8_Wrapper.pdf}
%\includegraphics[height=2in]{N58_rupt_0.pdf}
%\includegraphics[height=2in]{N58_rupt_200.pdf}
\\
%\includegraphics[height=2in]{N58_rupt_400.pdf}
%\includegraphics[height=2in]{N58_rupt_600.pdf}
  \caption{\label{figure8} Tank-treading leads to membrane rupture for
  large shear rates.} 
\end{figure}
A temporary fissure or a complete membrane rupture can occur at large
shear rates. Figure~\ref{figure8} demonstrates how a vesicle can rupture
when suspended in a shear flow. For $\chi = 0.1$, starting with a
circular shape (Figure~\ref{figure8}a), the vesicle is stretched by the
background flow and fissures appear in the bilayer structure in multiple
locations (Figure~\ref{figure8}b). In Figure~\ref{figure8}c, the
ruptured vesicles form two planar micelles which are eventually carried
off by the flow (Figure~\ref{figure8}d). 
%
\ReviewerOne{An emperical numerical study has shown that the critical shear rate for a complete membrane rupture is $\chi=0.0655$. Supplementary Materials Movie 4 shows the membrane rupture at the critical shear rate.}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{Figure6_Wrapper.pdf}
%\includegraphics[width=0.8\textwidth]{slipper.eps}
  \caption{\label{figure6} A JP vesicle placed in a parabolic flow
  drifts toward the central axis. It assumes a slipper shape and
  undergoes tank-treading motion like in the shear flow case. The arrows
  on the left illustrate the background flow and the arrows on the right
  show the velocity relative to the vesicle's moving frame. The thick
  black curve plots the distance from the axis as a function of time
  from left to right. The parameters are $v_{max} = 8$~nm ns$^{-1}$,
  $w=10$, and $R_0=20$ nm.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Increases in $\gamma$ and $M$ result in
a commensurate increase in the stretching modulus. 
Permeability, however, is insensitive to simultaneous increases in $\gamma$ and $M$.
To give a detailed explanation for this, the JP system has the potential energy $E = G + H$ where 
\begin{equation}
\label{eq:baseline_energy}
G = \gamma \int_{\Omega} \rho |\nabla u|^2 + \rho^{-1} u^2 \,dx,\quad H = M \sum_{i=1}^{N_b}\sum_{j \neq i} 
       P(|\tilde{\xx}_i - \tilde{\xx}_j|).
\end{equation}
Here, $G$ is the hydrophobic attraction potential for the boundary value problem \eqref{eq:SL}--\eqref{eq:SLff},
and $H$ is the repulsion potential.  
For the circular vesicle, total energy depends only on the characteristic inter-particle distance $x$
and has a minimum at $x_0$. 
If $\gamma$ and $M$ are scaled by $c$, 
we can related the scaled energy to that of the baseline case by 
\[E_c(x) = c(G(x) + H(x)).\]
Permeability does not change with like increases in $\gamma$ and $M$
because the critical number for $E_c$, and hence inter-particle separations, are independent to $c$.
The stretching modulus comes from $\frac{d^2E_c}{dx^2}$ and this 
quantity varies proportionally with $c$.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.97\textwidth]{Figure11_Wrapper_New.pdf}
%\includegraphics[width=0.9\textwidth]{ExtTraj.eps}
\end{center} 
  \caption{\label{figure11} The initial placement of two JP vesicles
  suspended in an extensional flow affects the long-time dynamics. The
  moving paths of the two centroids are plotted in blue in red. Each row
  corresponds to a different initial placement of the JP vesicles. (i)
  Both JP vesicle centroids are on the $x$-axis. (ii) The centroid of
  the left JP vesicle is $0.25$~nm above the $x$-axis and the right JP
  vesicle is on the $x$-axis. (iii) The centroid of the left JP vesicle
  is $0.25$~nm above the $x$-axis and the right JP vesicle is $0.25$~nm
  below the $x$-axis. (iv) The centroid of the left JP vesicle is
  $1.25$~nm above the $x$-axis and the centroid of the right JP vesicle
  is $1.25$~nm below the $x$-axis. The streamlines appear in grey and
  the flow rate is $\dot \gamma =0.005$~ns$^{-1}$ in all cases.}
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Figure12_Wrapper.pdf}
%\includegraphics[height=2in]{N116_ext_0.pdf}
%\includegraphics[height=2in]{N116_ext_2000.pdf}\\
%\includegraphics[height=2in]{N116_ext_4000.pdf}
%\includegraphics[height=2in]{N116_ext_6500.pdf}
  \caption{\label{figure12} The figure is for the simulation case (iii) of Figure~\ref{figure11},
  and additionally plots the pressure $p$.  The color bar is shared by all panels. 
  The insets of all panels are generated from simulations of a continuum
  model of the vesicles and the streamlines agree between the two models.}
\end{figure}

>>>>

% what we solve for?
\ReviewerOne{
\subsection{Time Marching}
To summarize, the proposed algorithm aims to obtain the JP velocities ${\bf v}_i$ and $\omega_i$. 
After calculating the imposed forces $\FF_i$ and torques $T_i$, 
two density functions $\sigma$ and  $\eeta$ are solved in the second-kind integral equations involving the HAP~\eqref{eq:screenedSKIE} and the mobility problem~\eqref{eq:SKIE}-\eqref{eq:mobility2} via GMRES.
%By solving the mobility problem, we obtain translational and angular
%velocities of the $N_b$-body system. 
Moreover, a second-order Adams-Bashforth
scheme updates the particle positions and orientations. By including the
repulsion force~\eqref{eq:REPULforce}, particle collisions can be avoided by setting time step
size $\Delta t\sim O(10^{-1})$.
%are avoided even when using a relatively larger time step than $\Delta t\sim O(10^{-1})$ ns. 
}

@@

%updated table
\begin{table}
\caption{Friction Coefficients $b$ (pN ns nm$^{-3}$) \\
}
\centering
\begin{tabular}{c c c c c c c c c c c c }
& & & & & & & $\dot\gamma$  (ns$^{-1}$) & & & &\\
\cline{1-11}\\
  radius ($l_0$) &  $\rho$ ($l_0$) & $\rho_0(l_0)$ & 0.0020   &  0.0025 &  0.0030 &  0.0035 &  0.0040 & 0.0045 & 0.0050  & Average\\
\cline{4-10}\\
& $+ 10 \%$ &     & 0.50  & 0.51  &  0.44 & 0.52  & 0.45 &  0.57   &  0.62 & 0.52  \\ 
& $+ 5 \%$ & & 0.54 & 0.41 & 0.35  & 0.37 & 0.43 & 0.76  & 0.70 & 0.51\\ 
0.5 &  2.0 & 0.5    & 0.42 & 0.63 & 0.50   & 0.40  & 0.48  & 0.53 & 0.55 & 0.50 \\   % new
& $- 5 \%$ &  & 0.22 & 0.36 & 0.41   & 0.45  & 0.45 & 0.44   & 0.44 & 0.40\\ 
\end{tabular} 
\label{table1}
\end{table}

@@

%Table~\ref{table1} provides $b = 0.79 \pm 0.3$ pN ns nm$^{-3}$  
\ReviewerOne{Table~\ref{table1} provides a series of numerical friction coefficients $b$ and the default number of particles is $N_b = 58$. With the fixed total length of the JP vesicle, we change parameters related to the length scale, for instances, $\rho$, $\rho_0$, and the radius of particles.
With $-5\%$, $5\%$, and $10\%$ adjustments in these parameters, the resulting numbers of particles are $N_b=\{61,56,53\}$, respectively. }
%
\ReviewerOne{The overall trend shown in Table~\ref{table1} is values of $b$ decreases as $\rho$
decreases and $b$ are}
%over a range of shear rates which is 
in good quantitative agreement with values previously reported in the literature.
Atomistic studies have also considered inter-monolayer slip in lipid bilayers. 
\cite{WuoEd06} and \cite{denOtter2007} reported $b = 0.7 \times 10^6$ Pa m$^{-1}$ s  
$=0.7$ pN ns nm$^{-3}$  
and $b = 2.4$  pN ns nm$^{-3}$ for DPPC membranes simulated by MD, respectively. 
Using a more recent version of the Martini force field, \cite{Zgorski2019} 
gives $b = 5.5$ pN ns nm$^{-3}$ for shear rates 0.4 ns$^{-1}$ and higher.
It is understandable that there is uncertainty in the friction coefficients of
Table~\ref{table1}.  The scatter in our data, however, is fully consistent with that calculated
from MD simulations, c.f. the transient rise in values of Table~\ref{table1} and in \cite{Zgorski2019}, Figure 10
for low shear rates. 
\subsubsection{Membrane Ruptures}
\begin{figure}
\centering
\includegraphics[width=11.32cm]{Figure8_Wrapper.pdf}
%\includegraphics[height=2in]{N58_rupt_0.pdf}
%\includegraphics[height=2in]{N58_rupt_200.pdf}
\\
%\includegraphics[height=2in]{N58_rupt_400.pdf}
%\includegraphics[height=2in]{N58_rupt_600.pdf}
  \caption{\label{figure8} Tank-treading leads to membrane rupture for
  large shear rates.} 
\end{figure}
A temporary fissure or a complete membrane rupture can occur at large
shear rates. Figure~\ref{figure8} demonstrates how a vesicle can rupture
when suspended in a shear flow. For $\chi = 0.1$, starting with a
circular shape (Figure~\ref{figure8}a), the vesicle is stretched by the
background flow and fissures appear in the bilayer structure in multiple
locations (Figure~\ref{figure8}b). In Figure~\ref{figure8}c, the
ruptured vesicles form two planar micelles which are eventually carried
off by the flow (Figure~\ref{figure8}d). 
%
\ReviewerOne{An emperical numerical study has shown that the critical shear rate for a complete membrane rupture is $\chi=0.0655$. Supplementary Materials Movie 4 shows the membrane rupture at the critical shear rate.}

@@

\begin{figure}
\centering
\includegraphics[width=\textwidth]{Figure6_Wrapper.pdf}
%\includegraphics[width=0.8\textwidth]{slipper.eps}
  \caption{\label{figure6} A JP vesicle placed in a parabolic flow
  drifts toward the central axis. It assumes a slipper shape and
  undergoes tank-treading motion like in the shear flow case. 
 \ReviewerThree{The horizontal dashed line represents time in units of $\mu$s and the vertical axis represents the scaled $y$ position of the centroid of the JP vesicle.}
  The arrows
  on the left illustrate the background flow and the arrows on the right
  show the velocity relative to the vesicle's moving frame. The thick
  black curve plots the distance from the axis as a function of time
  from left to right. The parameters are $v_{max} = 8$~nm ns$^{-1}$,
  $w=10$, and $R_0=20$ nm.}
\end{figure}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

Increases in $\gamma$ and $M$ result in
a commensurate increase in the stretching modulus. 
Permeability, however, is insensitive to simultaneous increases in $\gamma$ and $M$.
To give a detailed explanation for this, the JP system has the potential energy $E = G + H$ where 
\begin{equation}
\label{eq:baseline_energy}
G = \gamma \int_{\Omega} \rho |\nabla \ReviewerTwo{\eta}|^2 + \rho^{-1} \ReviewerTwo{\eta}^2 \,\dif\xx,\quad H = M \sum_{i=1}^{N_b}\sum_{j \neq i} 
       P(|\tilde{\xx}_i - \tilde{\xx}_j|).
\end{equation}
Here, $G$ is the hydrophobic attraction potential for the boundary value problem \eqref{eq:SL}--\eqref{eq:SLff},
and $H$ is the repulsion potential.  
For the circular vesicle, total energy depends only on the characteristic inter-particle distance $x$
and has a minimum at $x_0$. 
If $\gamma$ and $M$ are scaled by $c$, 
we can related the scaled energy to that of the baseline case by 
\[E_c(x) = c(G(x) + H(x)).\]
Permeability does not change with like increases in $\gamma$ and $M$
because the critical number for $E_c$, and hence inter-particle separations, are independent to $c$.
The stretching modulus comes from $\frac{d^2E_c}{dx^2}$ and this 
quantity varies proportionally with $c$.

@@

\begin{figure}
\begin{center}
\includegraphics[width=0.97\textwidth]{Figure11_Wrapper_New.pdf}
\end{center} 
  \caption{\label{figure11} The initial placement of two JP vesicles
  suspended in an extensional flow affects the long-time dynamics. The
  moving paths of the two centroids are plotted in blue in red. Each row
  corresponds to a different initial placement of the JP vesicles. (i)
  Both JP vesicle centroids are on the $x$-axis. (ii) The centroid of
  the left JP vesicle is $0.25$~nm above the $x$-axis and the right JP
  vesicle is on the $x$-axis. (iii) The centroid of the left JP vesicle
  is $0.25$~nm above the $x$-axis and the right JP vesicle is $0.25$~nm
  below the $x$-axis. (iv) The centroid of the left JP vesicle is
  $1.25$~nm above the $x$-axis and the centroid of the right JP vesicle
  is $1.25$~nm below the $x$-axis. The streamlines appear in grey and
  the flow rate is $\dot \gamma =0.005$~ns$^{-1}$ in all cases.
	  }
\end{figure}

\begin{figure}
  \centering
  \includegraphics[width=\textwidth]{Figure12_Wrapper.pdf}
  \caption{\label{figure12} The figure is for the simulation case (iii) of Figure~\ref{figure11},
  and additionally plots the pressure $p$.  The color bar is shared by all panels. 
  The insets of all panels are generated from simulations of a continuum
  model of the vesicles and the streamlines agree between the two models.}
\end{figure}
